\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-chakravarttyAccumulationDispossessionDebt2012a}{}}%
Chakravartty, Paula, and Denise Ferreira da Silva. 2012.
{``Accumulation, {Dispossession}, and {Debt}: The {Racial Logic} of
{Global Capitalism}---{An Introduction}.''} \emph{American Quarterly} 64
(3): 361--85. \url{https://www.jstor.org/stable/23273527}.

\leavevmode\vadjust pre{\hypertarget{ref-cumings1981}{}}%
Cumings, Bruce. 1981. \emph{The {Origins} of the {Korean War}:
Liberation and the Emergence of Separate Regimes, 1945-1947}.
{Yuksabipyungsa}. \url{https://books.google.com?id=3hJyAAAAMAAJ}.

\leavevmode\vadjust pre{\hypertarget{ref-eichengreen2011}{}}%
Eichengreen, Barry. 2011. \emph{Exorbitant {Privilege}: The {Rise} and
{Fall} of the {Dollar} and the {Future} of the {International Monetary
System}}. {Oxford University Press}.
\url{https://books.google.com?id=TIlpAgAAQBAJ}.

\leavevmode\vadjust pre{\hypertarget{ref-harveyNewImperialism2003}{}}%
Harvey, David. 2003. \emph{The {New Imperialism}}. {Oxford University
Press}.

\leavevmode\vadjust pre{\hypertarget{ref-1997a}{}}%
{``Issues of the Tonga Ilbo.''} 1997--1999. {The Tonga Ilbo}.
\url{https://newslibrary.naver.com/viewer/index.nhn?publishDate=1997-01-01\&officeId=00009\&pageNo=1}.

\leavevmode\vadjust pre{\hypertarget{ref-kohler2001}{}}%
Kohler, Horst. 2001. {``{IMF Managing Director Congratulates Korea} on
{Early Repayment} of 1997 {Stand}-{By Credit}.''} {The International
Monetary Fund}.
\url{https://archivescatalog.imf.org/Details/ArchiveExecutive/125150694}.

\leavevmode\vadjust pre{\hypertarget{ref-leeThineOwnselfBe2003a}{}}%
Lee, Catherine H. 2003. {``To {Thine Ownself Be True}: {IMF
Conditionality} and {Erosion} of {Economic Sovereignty} in the {Asian
Financial Crisis}.''} \emph{University of Pennsylvania Journal of
International Economic Law} 24: 875.
\url{https://heinonline.org/HOL/Page?handle=hein.journals/upjiel24\&id=885\&div=\&collection=}.

\leavevmode\vadjust pre{\hypertarget{ref-martin-jones2007}{}}%
Martin-Jones, David. 2007. {``Decompressing {Modernity}: South {Korean
Time Travel Narratives} and the {IMF Crisis}.''} \emph{Cinema Journal}
46 (4): 45--67. \url{https://www.jstor.org/stable/30137719}.

\leavevmode\vadjust pre{\hypertarget{ref-moon2005}{}}%
Moon, Seungsook. 2005. \emph{Militarized {Modernity} and {Gendered
Citizenship} in {South Korea}}. {Duke University Press}.
\url{https://doi.org/10.1515/9780822387312}.

\leavevmode\vadjust pre{\hypertarget{ref-economicsbureauoftherepublicofkorea1998}{}}%
Republic of Korea, Economics Bureau of the. 1998. {``Fiscal Reform Under
the {IMF} System.''}
\url{http://theme.archives.go.kr/viewer/common/archWebViewer.do?bsid=200041020104\&gubun=search}.

\leavevmode\vadjust pre{\hypertarget{ref-1998b}{}}%
{``Statement by {Mr}. {Zamani} on {Thailand} {EBM}/98/97.''} 1998.
\url{https://archivescatalog.imf.org/Details/ArchiveExecutive/125135004}.

\end{CSLReferences}
