\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-1997}{}}%
{``Asian {Crisis} - {Chronological Files}.''} {The International
Monetary Fund}, November 1997.
\url{https://archivescatalog.imf.org/Details/archive/110001667}.

\leavevmode\vadjust pre{\hypertarget{ref-1999a}{}}%
{``Asian {Crisis}, {General} - {Subject} Files: Criticisms of {Fund
Programs}.''} {The International Monetary Fund}, October 5--9, 1999.
\url{https://archivescatalog.imf.org/Details/archive/110002948}.

\leavevmode\vadjust pre{\hypertarget{ref-1998}{}}%
{``Asian {Crisis}, {General} - {Subject} Files: Financial {Sector},
{Economic Crises} and the {S}. {Fischer} Speech to {Conference} on
{Deposit Insurance}, {Washington D}.{C}.''} {The International Monetary
Fund}, September 10, 1998.
\url{https://archivescatalog.imf.org/results}.

\leavevmode\vadjust pre{\hypertarget{ref-1999}{}}%
{``Asian {Crisis}, {General} - {Subject} Files: Financial {System
Stability Assessments} ({FSSAs}).''} {The International Monetary Fund},
April 15--19, 1999.
\url{https://archivescatalog.imf.org/Details/ArchiveDescriptions/110032025}.

\leavevmode\vadjust pre{\hypertarget{ref-koreachamberofcommerceandindustry1997}{}}%
Commerce and Industry, Korea Chamber of. {``The {Impact} of the {IMF
Bailout} and {Our Response},''} December 1, 1997.
\url{http://theme.archives.go.kr/viewer/common/archWebViewer.do?bsid=200041030436\&gubun=search}.

\leavevmode\vadjust pre{\hypertarget{ref-2020}{}}%
{``Integrated {Public Use Microdata Series}, {International}: Version
7.3.''} {University of Minnesota Population Studies Center}, 2020.
\url{https://doi.org/10.18128/D020.V7.2}.

\leavevmode\vadjust pre{\hypertarget{ref-1997b}{}}%
{``Issues of the Kyunghang Newspaper.''} {Maeil-Gyungjae}, January
1997--December 1999.
\url{https://newslibrary.naver.com/viewer/index.nhn?publishDate=1997-01-01\&officeId=00020\&pageNo=1}.

\leavevmode\vadjust pre{\hypertarget{ref-1997c}{}}%
{``Issues of the Maeil-Gyungjae (Economics Daily).''} {Maeil-Gyungjae},
January 1997--December 1999.
\url{https://newslibrary.naver.com/viewer/index.nhn?publishDate=1997-01-01\&officeId=00009\&pageNo=1}.

\leavevmode\vadjust pre{\hypertarget{ref-1997a}{}}%
{``Issues of the Tonga Ilbo.''} {The Tonga Ilbo}, January 1997--December
1999.
\url{https://newslibrary.naver.com/viewer/index.nhn?publishDate=1997-01-01\&officeId=00009\&pageNo=1}.

\leavevmode\vadjust pre{\hypertarget{ref-zotero-138}{}}%
{``Monitoring of {Fund Arrangements Database}.''} {The International
Monetary Fund}, n.d.
\url{https://www.imf.org/external/np/pdr/mona/index.aspx}.

\leavevmode\vadjust pre{\hypertarget{ref-economicsbureauoftherepublicofkorea1998}{}}%
Republic of Korea, Economics Bureau of the. {``Fiscal Reform Under the
{IMF} System,''} December 20, 1998.
\url{http://theme.archives.go.kr/viewer/common/archWebViewer.do?bsid=200041020104\&gubun=search}.

\leavevmode\vadjust pre{\hypertarget{ref-economicsbureauoftherepublicofkorea1999}{}}%
---------. {``Two years of the IMF, as seen through statistics,''}
November 1999.
\url{http://theme.archives.go.kr/viewer/common/archWebViewer.do?bsid=200041048438\&gubun=search}.

\leavevmode\vadjust pre{\hypertarget{ref-1998a}{}}%
{``Speeches Files - "{Lessons} from the {Asian Financial Crisis}",
{Hubert Neiss CATO Institute}, {Washington}, {DC}. {Memos},
Pre-Conference Information.''} {The International Monetary Fund},
October 22, 1998.

\leavevmode\vadjust pre{\hypertarget{ref-zotero-139}{}}%
{``World {Integrated Trade Solutions Database}.''} {The World Bank and
the United Nations Statistical Division}, n.d.
\url{https://wits.worldbank.org/}.

\end{CSLReferences}
